{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}

### 2025-08-08 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

        Let $C \subseteq \RR^n$ be any closed and non-empty. 

@@

        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$. 
        Recall that $\nabla \varphi (x) = x - \bar x$. 

@@

    Furthermore, take note that $\Pi_C x \in D(x | C)$ always so, we have

@@

    \begin{assumption}[our assumptions]\label{ass:our-ass}

@@

            \item $g: \RR^n \rightarrow \RR$ is l.s.c

@@

@@

        Our hope is that the set $D$ is at least somewhat larger than $X^+$. 

@@

@@

            Consequently, the set of minimizers is the fixed point set of the alternating projection operators, $X^* = \Fix (\Pi_X \Pi_C)$. 

>>>>

        Let $C \subseteq \RR^n$ be any closed, non-empty and convex set. 

@@

        closed, convex, non-empty $C$ gives unique projection point so $\Pi_C$ is a convex set. 
        For notational simplicity let $\bar x = \Pi_C x, \bar y = \Pi_C y$, then it has $\nabla \varphi (x) = x - \bar x$. 

@@

    Furthermore, take note that $\Pi_C x \in D(x | C)$ is always true, hence we have

@@

    \begin{assumption}\label{ass:our-ass}

@@

            \item $g: \RR^n \rightarrow \RR$ is closed convex and proper. 

@@

    We take note that, under the above assumption the function $F = f + g$ is a $L_f$ weakly convex function and, $\widehat \partial F = \partial F$. 

@@

        Our hope is that the set $D$ is at least somewhat larger than $X^*$. 

@@

                \item The set $X^* = \Fix(\Pi_X \Pi_C) \neq \emptyset$. 

@@
